---
output:
  word_document: default
  html_document: default
---
# Module 2 - Assignment 2
## Black, Tyler
### Introduction to R Markdown


This document serves as an introduction to R Markdown. The R code in the 
following document will cover R data types, graphs, and common packages. The 
code produced here was introduced in an earlier assignment. 


The code underneath this paragraph plots two vectors, sales on the x-axis and
month on the y-axis using the package tidyverse and the function qplot.


```{r Plot of Sales by Month}
library(ggplot2)
library(tidyverse)
sales <- c(50,150,200,100,300,250)
month <- c(1,2,3,4,5,6)
qplot(month,sales)
```

What month had the largest sales? What was the amount? -> Month 5 and 300

```{r Working with Data Frames}
months <- c('Jan','Feb','Mar', 'Apr', 'May','Jun','Jul','Aug','Sep','Oct','Nov',
            'Dec')
month <- months
sales <- c(150.25, 258.54, 268.55, 122.52, 987, 458.82, 667.23, 845.54, 586.78, 
           888.58, 756.12, 456.84)
Yearly_Sales <- data.frame(month,sales)
qplot(Yearly_Sales$sales, Yearly_Sales$month)
```

Which month had the most sales? May       
Which month had the least sales? April

