---
output:
  word_document: default
  html_document: default
---
# Module 3 - Assignment 1

## Black, Tyler

### Data Visualization

In this assignment, we will be using the candy_data and candy_production data sets
to produce different graphs, including a scatter plot, line graph, and bar graph. 

```{r Loading Datasets}
library(tidyverse)
library(readr)
candy_data <- read_csv("candy_data.csv")
candy_production <- read_csv("candy_production.csv", 
    col_types = cols(observation_date = col_date(format = "%Y-%m-%d")))
```
#### Visualization with Scatterplots (geom_point)
```{r}
ggplot(data = candy_data,aes(x=sugarpercent,y=pricepercent,label=competitorname)) +
  geom_point() + 
  geom_smooth(method = "lm") +
  geom_text(check_overlap = T,# automatically reduce overlap (deletes some labels)
  vjust = "bottom", # adjust the vertical orientation
  nudge_y = 0.01, # move the text up a bit so it doesn't touch the points
  angle = 30,# tilt the text 30 degrees
  size = 2 # make the text smaller (to reduce overlap more)
  ) + # and then add labels to the points# 
  labs(title = "Sugar by Price Scatterplot", # plot title
  x = "Sugar content (percentile)", # x axis label
  y = "Price (percentile)" # y axis label
  )

```


It looks like Reese's stuffed with pieces is the most sugary candy with the lowest cost.
Reese's stuffed with pieces is the most sugary candy there is, but other candies are more expensive.  
Nestle Smarties is the most expensive candy with the most sugar. There are other candies that have more
sugar but they cost less. 


#### Line Chart of Candy Production
```{r Line Graph}
ggplot(data=candy_production, aes(x=observation_date,y=IPG3113N)) +
  geom_line() +
  geom_smooth() +
  labs(title = "Monthly Candy Production", # plot title
  x = "Year", # x axis label
  y = " As percent of 2012 production" # y axis label
  )
```

#### Bar Chart of Ingredients
```{r Bar Chart}
ggplot(data=candy_data,aes(x=chocolate)) +
  geom_bar()

# select out the columns that have the features of the candy (chocolate, caramel, etc.)
candyFeatures <- candy_data %>% select(2:10)
# make sure that these are booleans (logical)
candyFeatures[] <- lapply(candyFeatures, as.logical)

ggplot(data=candyFeatures,aes(x=chocolate)) +
  geom_bar()
```

