---
output:
  word_document: default
  html_document: default
---
# Module 6 - Assignment 2
## Black, Tyler
### Statistical Analyses

```{r Loading Packages}
library(tidyverse)
library(readxl)
Advertising <- read_csv("Advertising.csv")
Insurance <- read_csv("Insurance.csv")
Perceptions <- read_excel("Perceptions.xlsx")
RespiratoryExchangeSample <- read_excel("RespiratoryExchangeSample.xlsx")
```

### Regression and Correlation

*Regression analysis is a statistical method that allows you to examine the relationship between two or more
variables of interest. Correlation analysis is a method of statistical evaluation used to study the strength of a
relationship between two, numerically measured, continuous variables (e.g. height and weight). This
particular type of analysis is useful when a researcher wants to establish if there are possible connections
between variables.*

### Insurance Costs

*We would like to determine if we can accurately predict insurance costs based upon the factors included in
the data. We would also like to know if there are any connections between variables (for example, is age
connected or correlated to charges).*

### Correlations of bmi, age, children and cost

```{r Insurance}
Insurance2 <- select(Insurance, age, bmi, children, charges)
cor(Insurance2, use = 'everything', method = 'pearson')

library(corrplot)
library(RColorBrewer)
Corr_matrix <- cor(Insurance2, use = 'everything', method = 'pearson')
corrplot(Corr_matrix, type="upper", order="hclust",
col=brewer.pal(n=8, name="RdYlBu"))
```

Based on the matrix and visuals, explain the results from your correlation matrix in a paragraph after the
chunk of code. Are any of the variables highly correlated?   
**No, none of the variables are highly correlated to one another. Age and charges are the
'the most' correlated with a coefficient of .299, but this is not highly correlated**

### Regression Analysis

```{r Regression Analysis - Insurance}
charges_fit <- lm(charges ~ age + bmi + children, data = Insurance2)
summary(charges_fit)
```

Write a paragraph after the code. Based on the results, which variables were significant and what
particular significant variable had the largest impact on charges? Provide a summary after the chunk of
code.    
**All the variables are significant in terms of their p-value, but children have the biggest
impact on charges per its coefficient**


```{r Mutation}
Insurance <- mutate(Insurance, gender=ifelse(sex=="female",1,0))
Insurance <- mutate(Insurance, smoker2=ifelse(smoker=="yes",1,0))
Insurance3 <- select(Insurance,age,bmi,children,charges,gender,smoker2)
charges_fit2 <- lm(charges ~ age + bmi + children + gender + smoker2, data = Insurance3)
summary(charges_fit2)
```

After the code, provide an explanation of the new
results. Does gender and smoking have an impact on cost?   
**All the variables except *gender* have an impact on charges. Smoking has the highest impact **


### Group Comparisons with t-tests

*The t-test is used to compare the values of the means from two samples and test whether it is likely that the
samples are from populations having different mean values. This is often used to compare 2 groups to see if
there are any significant differences between these groups.*


### Caffeine Impacts on Respiratory Exchange Ratio

*A study of the effect of caffeine on muscle metabolism used volunteers who each underwent arm exercise
tests. Half the participants were randomly selected to take a capsule containing pure caffeine one hour
before the test. The other participants received a placebo capsule. During each exercise the subject's
respiratory exchange ratio (RER) was measured. (RER is the ratio of CO2 produced to O2 consumed and is an
indicator of whether energy is being obtained from carbohydrates or fats).
The question you are trying to answer is whether caffeine impacts RER during exercise.*

```{r Respiratory Results}
summary(RespiratoryExchangeSample)
t.test(RespiratoryExchangeSample$Placebo,RespiratoryExchangeSample$Caffeine)
```

Finally, interpret your results in a paragraph following the code. You can examine the p-value to see if
there was a significant difference between the groups.    
**Since the p-value is extremely large, we reject the null hypothesis in favor of the
alternative hypothesis that the difference in means is not equal to 0 (the groups have
different mean values)**


###  Impact of Advertising

*You are a marketing researcher conducting a study to understand the impact of a new marketing campaign.
To test the new advertisements, you conduct a study to understand how consumers will respond based on
see the new ad compared to the previous campaign. One group will see the new ad and one group will see
the older ads. They will then rate the ad on a scale of 0 to 100 as a percentage of purchase likelihood based
on the ad.
The question you are trying to answer is whether to roll out the new campaign or stick with the current
campaign.*

```{r Advertising}
summary(Advertising)
t.test(Rating ~ Group, Advertising, var.equal = TRUE)
```

 Finally, interpret your results in a paragraph following the code. You can examine the p-value to see if there
was a significant difference between the groups. You are trying to answer the question if the new
advertising campaign should move forward.   
**Since the p-value is quite large, we support the null hypothesis that the difference in means
is equal to zero, and we discourage the new advertising campaign. **

### ANOVA

An ANOVA test is a way to find out if survey or experiment results are significant. In other words, they help
you to figure out if you need to reject the null hypothesis or accept the alternate hypothesis. Basically, you’re
testing groups to see if there’s a difference between them. Examples of when you might want to test
different groups:   

- A group of psychiatric patients are trying three different therapies: counseling, medication and
biofeedback. You want to see if one therapy is better than the others.
- A manufacturer has two different processes to make light bulbs. They want to know if one process is
better than the other.
- Students from different colleges take the same exam. You want to see if one college outperforms the
other.


### Perceptions of Social Media Profiles

*This study examines how certain information presented on a social media site might influence perceptions of
trust, connectedness and knowledge of the profile owner. Specifically, participants were shown weak,
average and strong arguments that would influence their perceptions of the above variables. Using the
dataset provided, the following code runs an ANOVA with post-hoc analyses to understand argument
strength impacts on perceptions.*

```{r Anova}
anova1 <- aov(Trust ~ Argument, Perceptions)
summary(anova1)

anova2 <- aov(Connectedness ~ Argument, Perceptions)
summary(anova2)

anova3 <- aov(Knowledge ~ Argument,Perceptions)
summary(anova3)

TukeyHSD(anova1)
TukeyHSD(anova2)
```
 Examine the results in a paragraph after the code chunk, specifically looking at the p-value (Pr(>F)) to see
which of the ANOVAs above were significant. You should see that two of these ANOVAs are significant   
**The ANOVAs that are significant are, Trust ~ Argument and Connectedness ~ Argument.**

Based on your post-hoc analysis, add some additional text to the paragraph
explaining your results.   
**There are significant differences in Trust means between weak-average arguments and weak-strong
arguments. Additionally, there are significant differences in Connectedness means between weak-average
arguments and weak-strong arguments** 




