---
output:
  word_document: default
  html_document: default
---
# Module 3 - Assignment 2
## Black, Tyler
### Exploratory Data Analysis

```{r load Tidyverse}
library(tidyverse)
```

#### Diamond Color and Price
```{r Scatter Plot carat vs price}
ggplot(data=diamonds, aes(x=carat,y=price)) +
  geom_point()
```

1.) What do you notice from the scatterplot as the carat size increases?  
**When the carat size increases, the price also increases. However, after a certain carat size, 
the price isn't as dependent on the carat size**

2.) From the scatterplot, what carats are most represented within the diamonds dataset?   
**Most of the diamonds are between the .5 to 2.5 carat size per the scatter plot**

```{r Scatter Plot color vs. price}
ggplot(data=diamonds, aes(x=color,y=price)) + 
  geom_point()
```

Do you see any difference based solely on color? **I do not**

```{r Color Classes added}
ggplot(data=diamonds, aes(x=carat,y=price,color=color)) +
  geom_point()
```

1.) Does color impact the price?  
**Yes, color impacts price. A diamond can have a low carat size, but have the best
color ('D') and be just as expensive as the diamonds with the biggest carat size. However, if a diamond has
a big carat size, it can offset the diamond having the worst color ('J') and be as expensive as diamonds with
better colors**

2.) Are certain colors associated with carat size? Provide an example.   
**The best color diamonds (‘D’) seem to be associated with a low carat size. For example, diamonds with color
('D') and a carat size of 1 have many observations in the $15,000 price range. 
In contrast, the worst color diamonds (‘J’) seem to be associated with a bigger carat size. There are a few observations of diamonds with the worst color ('J') and a carat size of over 4 in the price range of over $15,000.** 

```{r Random Set}
dsample <- diamonds[sample(nrow(diamonds), 100), ]
ggplot(data=dsample, aes(x=carat,y=price,color=color)) +
  geom_point() +
  geom_smooth()
```

**PLEASE UPDATE IN .DOCX - DR.CUMMINGS IGNORE THIS LINE**  

**I think this chunk of code is harder to analyze than when using the entire data set.
Additionally, certain colors or a non-representative number of observations of each color class may be
chosen since the sample is random and only 100 observations.**


#### Additional Plots/Graphs
```{r Histograms}
ggplot(data=diamonds,aes(x=price, color = color)) +
  geom_histogram(binwidth = 250)

ggplot(data=diamonds,aes(x=carat, color = color)) +
  geom_histogram(binwidth = .5)
```

**I think these histograms do a great job of showing the distribution of diamond colors per carat size
and price. These histograms provide great evidence for the conclusions purported earlier**
