---
output:
  word_document: default
  html_document: default
---
# Module 6 - Assignment 1
## Black, Tyler
### Lubridate

```{r Loading Packages}
library(tidyverse)
library(lubridate)
Appointments <- read_csv("Appointments.csv")
```
### Working with Dates

```{r Formatting for Dates}
Appointments <- mutate(Appointments, ReservationYear = 2019)
Appointments <- mutate(Appointments, ReservationDate =
                       make_date (month=ReservationMonth, day=ReservationDay, year= ReservationYear))
Appointments <- mutate(Appointments, CreationDate =
                       make_date (month=CreationMonth, day=CreationDay, year= CreationYear))

Appointments <- mutate(Appointments, ReservationSpan = ReservationDate - CreationDate)
```

### Exploratory Analysis
```{r Exploratory Analysis}
summary(Appointments)
Appointments <- mutate(Appointments, ReservationSpan = as.numeric(ReservationSpan))
summary(Appointments)
```

a. What is the average time between appointment creation and the actual reservation date?  
**38.53 days**
b. What was the max time?   
**207 days**
c. What was the min time?    
**1 day**

```{r Correlation Analysis}
Appointments_Cor <- select(Appointments, ReservationSpan, Show)
cor(x=Appointments_Cor, use = 'everything', method = 'pearson')
cor(x=Appointments$ReservationSpan, y= Appointments$Show, use = 'everything', method = 'pearson')
```
a. Are ReservationSpan and Show highly correlated?     
**No, the data suggests they are independent of one another**





```{r Bar Chart}
ggplot(data=Appointments,mapping = aes(x=Show)) +
  geom_bar() +
  labs(title = 'Number of No Shows', x = '0 = No Show; 1 = Show')
```

a. Based on 0 being “no show” and 1 being “show”, did most people make their appointments?     
 **Most of the patients made their appointments**
 
 
 
 
