---
output:
  word_document: default
  html_document: default
---
# Module 4 - Assignment 1
## Black, Tyler
### Data Transformation

```{r TidyVerse and Loading Dataset}
library(tidyverse)
state_income <- read_csv("state_income.csv")
```
#### State Incomes

Subsets will be created from the state_income database. Different variables and
conditions will be used. Variables will also be renamed. A subset for just North
Carolina data will be created. 

```{r Select}
state_income2 <- select(state_income,State_Name, State_ab, County, City,
                        Type, ALand, Mean, Median, Stdev)
State_ab <- select(state_income2,State_ab,everything())
head(State_ab, n = 10)
```
```{r Rename}
state_income2 <- rename(state_income2,SquareArea = ALand, IncomeMean = Mean, 
                        IncomeMedian = Median, IncomeStdev = Stdev)
head(state_income2,n = 10)
```
```{r Filter}
NC_Income <- filter(state_income2,State_Name == 'North Carolina')
head(NC_Income, n =10)
```

#### NC Income  

The data set created earlier for just North Carolina data will be used to create
income summaries by county, city, and type. 

```{r Arrange}
NC_Income <- arrange(NC_Income,County)
head(NC_Income,n=10)
```
```{r Summary}
summary1 <- group_by(NC_Income,County)
summary1 <- summarise (summary1, mean= mean(IncomeMean))

summary2 <- NC_Income %>%
group_by(City) %>%
summarise (mean = mean(IncomeMean))
```
The summary1 data set groups the mean state incomes for North Carolina by county.    
Wake County has the highest mean state income.   
The summary2 data set groups the mean state incomes for North Carolina by city.
Davidson has the highest mean state income.

```{r Summary 3}
summary3 <- NC_Income %>%
group_by(Type) %>%
summarise (mean = mean(IncomeMean))
```

#### Income Visualization
```{r GGplot}
ggplot(data = summary1, aes(x=County,y=mean)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90,vjust =0.5, hjust=1)) +
  labs(title = 'Income By County',y= 'Income')
```

Within the R Markdown document, create a new paragraph that states which county has the largest average
income and which county has the lowest average income. Which has the second lowest income?  
**Wake County has the largest income while Stokes County has the lowest and Surry County had the
second to lowest**

```{r Average on AB}
AvgStateIncome <- state_income2 %>%
group_by(State_ab) %>%
summarise (mean = mean(IncomeMean))

AvgStateIncome <- filter(AvgStateIncome, grepl('N',State_ab))

ggplot(data=AvgStateIncome,aes(x=State_ab, y = mean)) +
  geom_point() +
  labs(title = 'Average Income for "N" Abbreivated States', x= 'State Abbreviation',
       y = 'Income')
```

**TN had the lowest average State Income while NJ had the largest State Income.** 

